---
title: "exp1.2_meltCurveGenotyping"
author: "Karissa Barthelson"
date: "2023-08-23"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---
```{r}
library(tidyverse)
library(readxl)
library(magrittr)
library(scales)

theme_set(theme_classic())
```

# Introduction

In this page, i will analyse the melt curve data generated on the qPCR machine to genotype at the *naglu* A603 site. In this genotyping assay, I amplify a ~70 bp region over the mutation site in each fish on the qPCR machine. I then perform a melt curva after the PCR amplification is complete. 

Since the  *naglu* A603fs mutation deletes 10 bp, the 2 PCR products arising from the mutant and wild type alleles will have a different melting temperature, and this can be observed in the melt curve. 

## read in data
```{r}
# read in the data

# melt cureve deriviities
dfs <- 
  read_delim("data/exp1.2/genotyping_data/KB_20230821_salbutamolExp1_2_nagluhomxhet7m_genotyping_meltregionderivativedata.txt", 
             delim = "\t", # tab delimited
             skip = 8) %>% 
  pivot_longer(names_to = "Reading",
               values_to = "dF",
               starts_with("Reading")
               ) %>%
  dplyr::select(Position = `Well Location`, Reading, dF)

# temperature readings
temps <- 
  read_delim("data/exp1.2/genotyping_data/KB_20230821_salbutamolExp1_2_nagluhomxhet7m_genotyping_meltregiontemperaturedata.txt",
                    delim = "\t", 
                    skip = 8
                    ) %>%
  pivot_longer(names_to = "Reading",
               values_to = "Temperature",
               starts_with("Reading")
               ) %>%
  dplyr::select(Position = `Well Location`, Reading, Temperature)

# normalised fluorescence from SYBR green data

fluordata <- 
  read_delim("data/exp1.2/genotyping_data/KB_20230821_salbutamolExp1_2_nagluhomxhet7m_genotyping_meltregionnormalizeddata.txt",
             delim = "\t", 
             skip = 8
  ) %>%
  pivot_longer(names_to = "Reading",
               values_to = "fluor.n",
               starts_with("Reading")
  ) %>%
  dplyr::select(Position = `Well Location`, Reading, fluor.n)



# results file
data.results <- 
  read_delim("data/exp1.2/genotyping_data/KB_20230821_salbutamolExp1_2_nagluhomxhet7m_genotyping_results.txt",
             delim = "\t", 
             skip = 8
  ) %>%
  dplyr::select(Position = Well, sample = `Sample Name`, Tm1, Tm2, Tm3) %>%
  mutate(group = case_when(
    Position == "A1" ~ "neg control",
    Position == "A2" ~ "het positive control",
    Position == "A3" ~ "hom positive control",
    TRUE ~ "unknown"
  ))




# metadata of this fish and ckeanup
meta <- read_excel("data/exp1.2/2023_Aug18_salbutamolexp1_2_meta.xlsx") %>%
  mutate(fish_id = as.character(fish_id),
         
         treatment = factor(treatment,
                            levels = c("untreated", "20 µM Salbutamol")),
         
         sex = as.factor(sex),
         
         behavBatch = as.factor(behavBatch),
         
         ymazeUnit = as.factor(ymazeUnit),
         
         ymazePosition = as.factor(ymazePosition)) %>%
  
  dplyr::select(fish_id, treatment, sex, Position = PositionForGeno, everything())



# join these together
data.meltcurve <-
  dfs %>%
  left_join(temps) %>% 
  left_join(fluordata) 
```

# Plot out fluorescence data

As the temp increases, the fluorescence decreaes. This is consistent with theee PCR products melting and the SYBR Green no longer fluorescing. 

```{r}
data.meltcurve %>%
  left_join(data.results) %>%
  ggplot(aes(x = Temperature, y = fluor.n), 
         alpha = 0.75) +
  geom_line(aes(group = Position,
                colour = group)) +
  scale_x_continuous(limits = c(78,86),
                     breaks = seq(70,90)) +
  scale_y_continuous(labels = comma)
```

# Plot out the first derivitive of the fluorescence data

Two clear peaks are observed consistent with the wt and mutant alleles being present. 
```{r}
data.meltcurve %>%
  left_join(data.results) %>%
  ggplot(aes(x = Temperature, y = dF)) +
  geom_line(aes(group = Position,
                size = group,
                alpha = group, 
                colour = group)) +
  scale_size_manual(values = c(2, 2, 2, 0.5)) + # make the controls fatter to stand out more
  scale_alpha_manual(values = c(1, 1, 1, 0.5)) + # make the unknowns more transparent so the controls stand out more. 
  scale_x_continuous(limits = c(78,86),
                     breaks = seq(70,90)) +
  scale_y_continuous(labels = comma, 
                     limits = c(0, 300000))
```

# define the hets and homs

```{r}
data.results <- data.results %>%
  mutate(wtallele = case_when(
    Tm1 > 81.9 ~ TRUE,  #if the melt temp is higher than 83C, this is the wt band and so het
    TRUE ~ FALSE
  ),
  mutallele = case_when(
    Tm1 < 81.9  ~ TRUE,
    TRUE ~ FALSE
  ),
  inferredGenotype = case_when(
    Position == "A1" ~ "neg control",
    Position == "A2" ~ "het positive control",
    Position == "A3" ~ "hom positive control",
     wtallele ==  TRUE & mutallele == FALSE ~ "het",
    wtallele ==  TRUE & mutallele == TRUE ~ "het",
    wtallele ==  FALSE & mutallele == TRUE ~ "hom"
  )
  )
```

# plot out the results by genotype

```{r}

# repeat the plot
data.meltcurve %>%
  left_join(data.results) %>%
  ggplot(aes(x = Temperature, y = dF)) +
  geom_line(aes(group = Position,
                size = group,
                alpha = group, 
                colour = inferredGenotype)) +
  scale_size_manual(values = c(2, 2, 2, 0.5)) + # make the controls fatter to stand out more
  scale_alpha_manual(values = c(1, 1, 1, 0.5)) + # make the unknowns more transparent so the controls
  scale_x_continuous(limits = c(78,86),
                     breaks = seq(70,90)) +
  scale_y_continuous(labels = comma, 
                     limits = c(0, 300000))

```

# export the data 
```{r}
# export data for the final document
meta %>%
  left_join(data.results %>%
              dplyr::select(Position, genotype = inferredGenotype)) %>%
  dplyr::select(1,2,3, genotype, everything()) %>%
  saveRDS("data/exp1.2/metadata_withGenotype.rds")

data.meltcurve %>%
  left_join(data.results) %>%
  saveRDS("data/exp1.2/genotyping_data/meltcurveWithGenotypes.rds")

```


