---
title: "fullexp13"
author: "Karissa Barthelson"
date: "2024-01-12"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  autodep = TRUE,
  echo = TRUE, 
  warning = FALSE,
  message = FALSE,
  fig.align = "center", 
  fig.retina = 1,
  out.width ="100%", 
  out.height = "100%"
)
```

```{r packages}
library(tidyverse)
library(readxl)
library(here)
library(magrittr)
library(scales)
library(readxl)
library(ggpubr)
library(ggeasy)
library(ggfortify)
library(ggbeeswarm)
library(ggforce)
library(ggrepel)
library(kableExtra)

# stat analysis
library(broom)
library(lme4)
library(performance)
library(car)
library(emmeans)
library(glmmTMB)
library(MASS)

# set the default theme for ggplot as theme_bw
theme_set(theme_classic())
```

# Introduction

In this experiment, i treated equal roughly numbers of male and female fish with and without 20 uM of salbutamol. Then, they were subjected to the FMP ymaze test. Then i genotyped the fish.

here, i will analyse the behaviour data

# genotyping summary

The genotying data was properly analysed in a seperate R script `code / experiment 1/ exp1_genotypingMeltCurve.R`. However, the results are shown here.

```{r}
read_rds("data/exp1.3/genotyping_data/meltcurveWithGenotypes.rds") %>% 
  ggplot(aes(x = Temperature, y = dF)) +
  geom_line(aes(group = Position,
                colour = genotype)) +
  scale_x_continuous(limits = c(78,86),
                     breaks = seq(70,90)) +
  scale_y_continuous(labels = comma, 
                     limits = c(0, 170000)) 
```

# metadata summary

The following plot shows the number of fish per genotype, treatment and sex.

```{r}
meta <- 
  readRDS("data/exp1.3/metadata_withGenotype.rds") %>% 
  dplyr::filter(genotype %in% c("het", "hom")) %>% 
  mutate(sex = case_when(
    grepl(sex, pattern = "m") ~ "m", 
    TRUE ~ sex
  ))
```

```{r}
meta %>% 
  ggplot(aes(x = treatment, fill = genotype)) +
  geom_bar(position = "dodge") +
  facet_wrap(~sex) +
  scale_y_continuous(breaks = seq(1,26))
```

# behavaiour data analysis

## read in the pre-processed data

```{r}
final_data <- read_csv("data/exp1.3/processed_data/final_output.csv") %>% 
  dplyr::select(-1) %>% 
  mutate(fish_id = as.character(fish_id)) %>% 
  left_join(meta) %>% 
  dplyr::filter(genotype %in% c("het", "hom"), 
                sex %in% c("m", "f"))

# make an object which converts the final data to long format. for easier plotting in ggplot
final_data_long <- final_data %>%
  gather(key = "tetras", value = "Count", # convert to long format
         grep("[L|R]{4}", 
              colnames(.))
         )

# also make an object which sums the tetragrams over the hour
final_data_summedoverbins <- final_data %>%
  gather(key = "tetras", value = "Count", # convert to long format
         grep("[L|R]{4}", # select the columns which contain a L or a R four times
              colnames(.))
         ) %>% 
  group_by(fish_id, tetras) %>% 
  mutate(x = sum(Count)) %>% # sum the tetragram counts per fish_id
  dplyr::select(colnames(meta), tetras, x) %>% 
  unique

distancess <- read_rds("data/exp1.3/processed_data/distanceDataexp1-3.rds") 

# 6 min bins
bin_df <- tibble(
  # 10 min buins 
  bins6 = c(rep(1, 600), 
            rep(2, 600), 
            rep(3, 600), 
            rep(4, 600), 
            rep(5, 600), 
            rep(6, 600)
  ) %>% as.factor(), 
  BIN_NUM = distancess$BIN_NUM %>% unique)
```

## assess proper tracking

First need to have a look at whether tracking worked nicely for these fish. To do this, I will import the distance data and plot it out. I also have the videos saved to double check anything strange.

```{r}
distancess %>%
  left_join(bin_df) %>% 
  group_by(fish_id, bins6) %>% 
  mutate(total_distance = sum(TOTAL_DISTANCE_IN_ZONE)) %>% 
  dplyr::distinct(bins6, .keep_all = T) %>% 
  dplyr::filter(genotype %in% c('het', 'hom'), 
                sex %in% c("m", "f")) %>%
  ggplot(aes(x = bins6, y = total_distance)) +
  geom_jitter(alpha = 0.75) +
  geom_boxplot(aes(x = bins6), 
               fill = NA) +
  geom_label(aes(label = fish_id), 
             data = . %>% 
               dplyr::filter(total_distance > 25000))
```

Several fish appear to have dodgy tracking. For this analysis I will just omit them. But I'm going to try tracking the data myself using [sleap.ai](sleap.ai).

To omit these fish, I will define that tracking did not work if a fish travelled more than 25000 cm (i.e. 250m in any of the 10 min bin).

```{r}
fish2omit <- distancess %>%
  left_join(bin_df) %>% 
  group_by(fish_id, bins6) %>% 
  mutate(total_distance = sum(TOTAL_DISTANCE_IN_ZONE)) %>% 
  dplyr::distinct(bins6, .keep_all = T) %>% 
  dplyr::filter(total_distance > 25000) %>% 
  .$fish_id %>% 
  unique
```

```{r}
distancess %>%
  left_join(bin_df) %>% 
  group_by(fish_id, bins6) %>% 
  mutate(total_distance = sum(TOTAL_DISTANCE_IN_ZONE)) %>% 
  dplyr::distinct(bins6, .keep_all = T) %>% 
  dplyr::filter(genotype %in% c('het', 'hom'), 
                sex %in% c("m", "f")) %>%
  dplyr::filter(!fish_id %in% fish2omit ) %>% 
  ggplot(aes(x = bins6, y = total_distance)) +
  geom_jitter(alpha = 0.75) +
  geom_boxplot(aes(x = bins6), 
               fill = NA) +
  geom_label(aes(label = fish_id), 
             data = . %>% 
               dplyr::filter(total_distance > 25000))
```

## omit problmeatic fish

```{r}
fish2omit3 <- c(
  fish2omit,
  meta %>% 
    dplyr::filter((genotype %>% is.na)) %>% .$fish_id
)


distancess %<>% 
  dplyr::filter(!(fish_id %in% fish2omit3))

final_data %<>% 
  dplyr::filter(!(fish_id %in% fish2omit3))

final_data_long %<>% 
  dplyr::filter(!(fish_id %in% fish2omit3))

final_data_summedoverbins %<>% 
  dplyr::filter(!(fish_id %in% fish2omit3))
  
```

# trial effects

Fish were tested across a whole day (from \~10am to 5pm) so circadian differences could be present here. Plot out total distance by trial. Trial specific effects are seen, but no clear pattern.

```{r}
distancess %>%
  left_join(bin_df) %>% 
  group_by(fish_id) %>% 
  mutate(total_distance = sum(TOTAL_DISTANCE_IN_ZONE)) %>% 
  dplyr::distinct(fish_id, .keep_all = T) %>% 
  dplyr::filter(!is.na(behavBatch)) %>% 
  ggplot(aes(y = total_distance, 
             x = bins6)) +
  geom_jitter(alpha = 0.75) +
  geom_boxplot(
    fill = NA, 
    outlier.colour = NA) +
  scale_y_continuous(labels = comma) +
  facet_wrap(~behavBatch, scales = "free_x", nrow = 1)
```

# total distance travelled

```{r}
fit.dists <- 
  distancess %>%
  left_join(bin_df) %>% 
  group_by(fish_id, bins6) %>% 
  mutate(total_distance = sum(TOTAL_DISTANCE_IN_ZONE)) %>% 
  dplyr::distinct(bins6, .keep_all = T) %>% 
  lmer(total_distance ~ (genotype*treatment*bins6*sex) + (1|behavBatch) +(1|fish_id), 
       data = .)

# check assumptions
# all look ok
check_model(fit.dists)

# colinearity
check_collinearity(fit.dists) %>% 
  plot +
  easy_rotate_x_labels(angle = -45)

an <- Anova(fit.dists)

emmeans(fit.dists, list(pairwise ~ genotype * treatment * sex), adjust = "tukey")

# geno treat sex
print(emmeans(fit.dists, ~ genotype * treatment * sex), type = "response") %>% 
  as_tibble() %>% 
  ggplot(aes(x = treatment, y = emmean, colour = genotype)) +
  geom_col(aes(fill = genotype), 
           alpha = 0.75,
           width = 0.75,
           position = position_dodge(width = 0.75)) +
  geom_errorbar(aes(ymin =  lower.CL, ymax = upper.CL),
                width = 0.5, 
                position = position_dodge(width = 0.75)) +
  facet_wrap(~sex, nrow = 1)

# geno treat
print(emmeans(fit.dists, ~ genotype * treatment), type = "response") %>% 
  as_tibble() %>% 
  ggplot(aes(x = treatment, y = emmean/100, colour = genotype)) +
  geom_col(aes(fill = genotype), 
           alpha = 0.75,
           position = position_dodge()) +
  geom_errorbar(aes(ymin =  lower.CL/100, ymax = upper.CL/100),
                position = position_dodge()) +
  facet_wrap(~treatment, nrow = 1, scales = "free_x") +
  labs(title = "7 days on salbutamol", 
       y = "Average distance travelled\nper 10 min bin (cm)") 

# geno treat bin
print(emmeans(fit.dists, ~ genotype * treatment * bins6 * sex), 
      type = "response") %>% 
  as_tibble() %>% 
  mutate(group = paste0(genotype, "_", 
                        treatment, "_", 
                        sex), 
         genotreat = paste0(genotype, "_", treatment)) %>% 
  dplyr::filter(genotreat != "het_20 µM Salbutamol") %>% 
  ggplot(aes(x = bins6, y = emmean, colour = genotreat)) +
  geom_point(aes(fill =group), 
           alpha = 0.75,
           position = position_dodge(width = 0.75)) +
  geom_errorbar(aes(ymin =  lower.CL, ymax = upper.CL),
                position = position_dodge(0.75)) +
  geom_line(aes(group = group), 
            position = position_dodge(0.75),
            show.legend = F) +
  facet_wrap(~sex, 
             scales = "free_x")
```

```{r}

```

# check for handedness

Fontana et al. (<https://doi.org/10.1007/s10071-019-01296-9>, Matt Parker's group) showed that fish sometimes show a behavioural lateralisation (i.e. handedness). If fish show this, then they would perform less alternation tetragrams not due to working memory. The plot below circles each of the L_R bias groups.

```{r}
# make the LR bias object
LR_Bias <- final_data %>%
  dplyr::select(L, R, total_turns, fish_id) %>%
  group_by(fish_id) %>%
  mutate(L = sum(L),
         R = sum(R),
         total_turns = sum(total_turns),
         L_R_bias = case_when( #consider more than 60% of the time performing a left or right turn to be a bias
           L/total_turns > 0.6 ~ "Left",
           R/total_turns > 0.6 ~ "Right",
           TRUE ~ "Neither"
         )) %>%
  dplyr::select(fish_id, L_R_bias) %>%
  unique() %>%
  mutate(L_R_bias = factor(L_R_bias,
                           levels = c("Neither", "Left", "Right"))
  )
```

The overall propotions of fish showing left, right or no bias is simialr across the 4 experimental groups.

```{r}
final_data %>%
  left_join(LR_Bias) %>%
  group_by(fish_id) %>%
  mutate(L = sum(L),
         R = sum(R),
         total_turns = sum(total_turns), 
         genotreat = paste0(genotype, "_", treatment)
        
  ) %>% 
  ggplot(aes(x = genotreat, fill = L_R_bias )) +
  geom_bar()
```

```{r}
# add the LR bias object to final data
final_data %<>% 
  left_join(LR_Bias) 
```

# test for changes to alternation

Cleal et al. showed that zebrafish naturally perform more of the alternation tetragrams (LRLR and RLRL) in a Y-maze. This is clearly observed here.

```{r}
final_data_summedoverbins %>%
  dplyr::distinct(x, .keep_all = T) %>%
  ggplot(aes(x = tetras, y = x)) +
  geom_jitter(aes(colour = tetras,
                  shape = sex)) +
  geom_boxplot(outlier.shape = NA,
               fill = NA
               ) +
  scale_fill_viridis_d() +
  labs(y = "Number of tetragrams",
       colour = "Tetragram",
       x = "Tetragram")+
  theme(legend.position = "bottom")  +
  ggtitle("Total number of 16 possible tetragrams performed by zebrafish in a Y-maze\nduring a 1 hour search period") 
  # geom_label_repel(aes(label = fish_id), 
  #                  data = . %>% 
  #                    dplyr::filter(x > 500))
```

We can also overlay the genotype boxplots as shown below. Looks like the heterozyous and homozygous fish perform more alternations than the WT fish. I will look into this more later in the analysis

```{r}
final_data_summedoverbins %>%
  ggplot(aes(x = tetras, y = x)) +
  geom_jitter(aes(colour = tetras,
                  shape = sex)) +
  geom_boxplot(outlier.shape = NA,
               aes(fill = genotype),
               alpha = 0.5,
               ) +
  scale_fill_viridis_d() +
  labs(y = "Number of tetragrams",
       colour = "Tetragram",
       x = "Tetragram")+
  theme(legend.position = "bottom")  +
  facet_wrap(~treatment, ncol = 1) +
  easy_rotate_x_labels(angle = -45) +
  annotate("rect", # add some boxes aeround the alts 
           xmin = 5.5, xmax = 6.5, 
           ymin = -1, ymax = 200, 
             alpha = 0, color= "red") +
  annotate("rect", 
           xmin = 10.5, xmax = 11.5, 
           ymin = -1, ymax = 200,
           alpha = 0, color= "red") +
  ggtitle("Total number of 16 possible tetragrams performed by zebrafish in a Y-maze\nduring a 1 hour search period") 
```

The alternation tetragrams are the tetragram of interest (the measure of working memory). Below indicates the number of tetragrams performed by zerbafish across the 6 x 10 min blocks of the hour they spent in the maze.

```{r}
final_data_long %>%
  dplyr::distinct(fish_id, bin, .keep_all = T) %>%
  mutate(binforvis = case_when(
    bin == 1 ~ "0-10 mins", 
    bin == 2 ~ "10-20 mins", 
    bin == 3 ~ "20-30 mins", 
    bin == 4 ~ "30-40 mins", 
    bin == 5 ~ "40-50 mins", 
    bin == 6 ~ "50-60 mins"
    )) %>% 
  ggplot(aes(x = treatment, y = alts)) +
  geom_boxplot(outlier.shape = NA,
               aes(fill = genotype), 
               alpha = 0.5) +
  geom_point(aes(colour = genotype), 
             position = position_jitterdodge()) +
  facet_wrap(~binforvis, nrow = 1) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), 
        legend.position = "bottom") +
  ylab("Frequency of alternation tetragrams (LRLR + RLRL)") +
  scale_colour_viridis_d(end = 0.75) +
  scale_fill_viridis_d(end = 0.75) 
  
```

We can also display this as the *relative* amount of alternation tetragrams performed by zebrafish in a 1 hour search period. This will control for how active each fish is. Again, fish 18 and 24 looks like outliers.

```{r}
final_data_long %>%
  dplyr::distinct(fish_id, bin, .keep_all = T) %>%
  mutate(binforvis = case_when(
    bin == 1 ~ "0-10 mins", 
    bin == 2 ~ "10-20 mins", 
    bin == 3 ~ "20-30 mins", 
    bin == 4 ~ "30-40 mins", 
    bin == 5 ~ "40-50 mins", 
    bin == 6 ~ "50-60 mins"
    )) %>% 
  ggplot(aes(x = treatment, y = rel_alts)) +
  geom_boxplot(outlier.shape = NA,
               aes(fill = genotype), 
               alpha = 0.5) +
  geom_point(aes(colour = genotype), 
             position = position_jitterdodge()) +
  facet_wrap(~binforvis, nrow = 1) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), 
        legend.position = "bottom") +
  ylab("Relative number of alternation tetragrams\n(LRLR + RLRL) / total_turns") +
  scale_colour_viridis_d(end = 0.75) +
  scale_fill_viridis_d(end = 0.75) 
```

Finally, I will now test for alternation changes using a generalised linear mixed effect model (beta-binomial distribution). We use this because it is count data which is over-dispersed, and fixed and random effects are included. The link function is logit. No significant effects are observed on working memory. Only the `L_R_bias` term is significant, this is to be expected, as they would probably be performing more repitiions. The `bin:Genotype` effect is close (ish) to statistical significance. Meaning that this might have something there. but this does not take into account the Treatment group.\
Note that I have ignored the effect of Sex here. We have never really seen a Sex effect in all of our ymaze analyses.

```{r}
glm <-
  final_data %>%
  left_join(LR_Bias) %>%
  mutate(
    non_alts = total_turns - alts,
    bin = as.factor(bin)
  ) %>%
  glmmTMB(
    cbind(alts, non_alts) ~ (bin + genotype + treatment + sex)^3 + L_R_bias + (1|behavBatch) + (1|fish_id),
    family = betabinomial(),
    data = .
  )
Anova(glm) %>%
  as.data.frame() %>%
  dplyr::rename(pval = `Pr(>Chisq)`) %>%
  kable() %>%
  kable_styling(full_width = FALSE) %>% 
  row_spec(row = 4, bold = TRUE)
```

## Vis

### genotype x treatment

The effect of genotype x treatment is not too far off statistical significance (p = 0.17) and is trending towards a rescue.

```{r}
print(emmeans(glm, ~ genotype * treatment * sex), type = "response") %>% 
  as_tibble() %>% 
  ggplot(aes(x = treatment, y = prob, colour = genotype)) +
  geom_col(aes(fill = genotype), 
           alpha = 0.5,
           width = 0.75,
           position = position_dodge()) +
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL ),
                width = 0.125,
                size = 1,
                position = position_dodge(width = 0.75)) +
  facet_wrap(~sex ) +
  theme(axis.text.x = element_text(hjust = 1,
                               vjust = 1,
                               angle = 45), 
        legend.position = "bottom") +
  scale_color_viridis_d(end = 0.8, option = "inferno") +
  scale_fill_viridis_d(end = 0.8, option = "inferno") +
  labs(y = "Estimated probability of alternation\n(LRLR + RLRL)",
       x = "genotype", 
       title = "GLM predicted probability of zebrafish performing an alternation\ntetragram due to Genotype and Treatment"
       )
```

### bin x Genotype x Treatment

While this is not significant, the homs treated with iron appear to be performing more alternations more like their het saline siblings

```{r}
print(emmeans(glm, ~ genotype * treatment * bin), type = "response") %>% 
  as_tibble() %>% 
  mutate(binforvis = case_when(
    bin == 1 ~ "0-10 mins", 
    bin == 2 ~ "10-20 mins", 
    bin == 3 ~ "20-30 mins", 
    bin == 4 ~ "30-40 mins", 
    bin == 5 ~ "40-50 mins", 
    bin == 6 ~ "50-60 mins"
    )) %>% 
  ggplot(aes(x = binforvis, y = prob, colour = genotype)) +
  geom_col(aes(fill = genotype), 
           alpha = 0.5,
           # width = 0.75,
           position = position_dodge()
           ) +
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL ),
                # width = 0.125,
                size = 1,
                position = position_dodge()) +
  facet_wrap(~treatment, nrow = 1) +
  theme(axis.text.x = element_text(hjust = 1,
                               vjust = 1,
                               angle = 45), 
        legend.position = "bottom") +
  scale_color_viridis_d(end = 0.8, option = "inferno") +
  scale_fill_viridis_d(end = 0.8, option = "inferno") +
  labs(y = "Estimated probability of alternation\n(LRLR + RLRL)",
       x = "Time interval", 
       title = "GLM predicted probability of zebrafish performing an alternation\ntetragram due to Genotype and Treatment", 
       subtitle = "p = 0.25"
       )
```

# test for changes to repitition

```{r}
final_data_long %>%
  dplyr::distinct(fish_id, bin, .keep_all = T) %>%
  mutate(binforvis = case_when(
    bin == 1 ~ "0-10 mins", 
    bin == 2 ~ "10-20 mins", 
    bin == 3 ~ "20-30 mins", 
    bin == 4 ~ "30-40 mins", 
    bin == 5 ~ "40-50 mins", 
    bin == 6 ~ "50-60 mins"
    )) %>% 
  ggplot(aes(x = treatment, y = rel_alts)) +
  geom_boxplot(outlier.shape = NA,
               aes(fill = genotype), 
               alpha = 0.5) +
  geom_point(aes(colour = genotype), 
             position = position_jitterdodge()) +
  facet_wrap(~binforvis, nrow = 1) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), 
        legend.position = "bottom") +
  ylab("Relative number of alternation tetragrams\n(LRLR + RLRL) / total_turns") +
  scale_colour_viridis_d(end = 0.75) +
  scale_fill_viridis_d(end = 0.75) 
```

Finally, I will now test for alternation changes using a generalised linear mixed effect model (beta-binomial distribution). We use this because it is count data which is over-dispersed, and fixed and random effects are included. The link function is logit. No significant effects are observed on working memory. Only the `L_R_bias` term is significant, this is to be expected, as they would probably be performing more repitiions. The `bin:Genotype` effect is close (ish) to statistical significance. Meaning that this might have something there. but this does not take into account the Treatment group.\
Note that I have ignored the effect of Sex here. We have never really seen a Sex effect in all of our ymaze analyses.

```{r}
glm.reps <-
  final_data %>%
  left_join(LR_Bias) %>%
  mutate(
    non_reps = total_turns - reps,
    bin = as.factor(bin)
  ) %>%
  glmmTMB(
    cbind(reps, non_reps) ~ (bin + genotype + treatment + sex)^3 + L_R_bias + (1|behavBatch) + (1|fish_id),
    family = betabinomial(),
    data = .
  )
Anova(glm.reps) %>%
  as.data.frame() %>%
  dplyr::rename(pval = `Pr(>Chisq)`) %>%
  kable() %>%
  kable_styling(full_width = FALSE) %>% 
  row_spec(row = 4, bold = TRUE)
```

## Vis

### genotype x treatment

The effect of genotype x treatment is not too far off statistical significance (p = 0.17) and is trending towards a rescue.

```{r}
print(emmeans(glm.reps, ~ genotype * treatment * sex), type = "response") %>% 
  as_tibble() %>% 
  ggplot(aes(x = treatment, y = prob, colour = genotype)) +
  geom_col(aes(fill = genotype), 
           alpha = 0.5,
           width = 0.75,
           position = position_dodge()) +
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL ),
                width = 0.125,
                size = 1,
                position = position_dodge(width = 0.75)) +
  facet_wrap(~sex ) +
  theme(axis.text.x = element_text(hjust = 1,
                               vjust = 1,
                               angle = 45), 
        legend.position = "bottom") +
  scale_color_viridis_d(end = 0.8, option = "inferno") +
  scale_fill_viridis_d(end = 0.8, option = "inferno") +
  labs(y = "Estimated probability of alternation\n(LRLR + RLRL)",
       x = "genotype", 
       title = "GLM predicted probability of zebrafish performing an alternation\ntetragram due to Genotype and Treatment"
       )

#em. <- emmeans(glm, list(pairwise ~ genotype * treatment), response) 

#em$`pairwise differences of genotype, treatment`

```

### bin x Genotype x Treatment

While this is not significant, the homs treated with iron appear to be performing more alternations more like their het saline siblings

```{r}
print(emmeans(glm.reps, ~ genotype * treatment * bin), type = "response") %>% 
  as_tibble() %>% 
  mutate(binforvis = case_when(
    bin == 1 ~ "0-10 mins", 
    bin == 2 ~ "10-20 mins", 
    bin == 3 ~ "20-30 mins", 
    bin == 4 ~ "30-40 mins", 
    bin == 5 ~ "40-50 mins", 
    bin == 6 ~ "50-60 mins"
    )) %>% 
  ggplot(aes(x = binforvis, y = prob, colour = genotype)) +
  geom_col(aes(fill = genotype), 
           alpha = 0.5,
           # width = 0.75,
           position = position_dodge()) +
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL ),
                # width = 0.125,
                size = 1,
                position = position_dodge()) +
  facet_wrap(~treatment, nrow = 1) +
  theme(axis.text.x = element_text(hjust = 1,
                               vjust = 1,
                               angle = 45), 
        legend.position = "bottom") +
  scale_color_viridis_d(end = 0.8, option = "inferno") +
  scale_fill_viridis_d(end = 0.8, option = "inferno") +
  labs(y = "Estimated probability of alternation\n(LRLR + RLRL)",
       x = "Time interval", 
       title = "GLM predicted probability of zebrafish performing an alternation\ntetragram due to Genotype and Treatment", 
       subtitle = "p = 0.25"
       )
```

# conclusion

Looks like 20 uM of salbutamol can affect zebrafish behaviour.

# export data

```{r}
final_data %>% 
  saveRDS("data/R_objects/tetras-exp1-3.rds")

distancess %>% 
  saveRDS("data/R_objects/distance_data-exp1-3.rds")
```
